\documentclass[12pt]{article}

\input{../kz}

\rhead{CS 180}

\begin{document}

\section{Topological Ordering or Cycle}

\subsection*{Algorithm}

\begin{algorithmic}[1]
    \State Run the standard DAG toposort algorithm
    \If{All nodes have been added}
        \State \Return computed topological order
    \EndIf
    \State Do another run of the toposort algorithm on the \textit{reversed} graph

    \item[]
    \State $v \gets$ any node that is in neither toposort's already sorted nodes
    \State $\texttt{frontier} \gets \text{empty queue}$
    \State $\texttt{comeFrom} \gets \text{array of size }n\text{, all nil}$
    \State Add $v$ to $\texttt{frontier}$
    \While{\texttt{comeFrom}[v] is nil}
        \State $\texttt{curr} \gets \text{popped front of }\texttt{frontier}$
        \ForAll{$n \in$ \texttt{curr}'s neighbors}
            \If{$\texttt{comeFrom}[n]$ is nil}
                \State $\texttt{comeFrom}[n] = \texttt{curr}$
                \State Add $n$ to $\texttt{frontier}$
            \EndIf
        \EndFor
    \EndWhile

    \item[]
    \State Trace back cycle starting from $v$
    \State \Return the computed cycle
\end{algorithmic}

\subsection*{Complexity}

The first section runs in $O(m+n)$ time, as has already been established in class.
The second section runs a multi-source BFS from all the neighbors of $v$.
Besides that the initial queue has more than one node, all other aspects
of the BFS are identical to the one we already came up with,
so the time complexity of this section is $O(m+n)$.

Finally, tracing back the cycle will take time proportional to the length of the cycle.
Since the cycle can have at most $n$ nodes, the complexity of this is $O(n)$.

Adding these complexities together,
we see that the overall time complexity is $O(m+n)$.

\pagebreak

\section{Deleting a Node to Destroy All Paths}

\subsection*{Proof of Existence}

SWOC the $v$ supposed in the problem doesn't exist.
Then, there must be two disjoint paths from $s$ to $t$.
Each path must have strictly greater than $\frac{n}{2}-1$ intermediary nodes,
and since none of the paths intersect, this means
\[|V| > 2\left(\frac{n}{2}-1\right)+2 = n\]
Contradiction, since $|V|=n$ by definition. $\square$

\subsection*{Algorithm}

\begin{algorithmic}[1]
    \State $L_0 \gets \{s\}$
    \State $\texttt{dist} \gets 0$
    \State Mark $s$ as explored
    \While{$L_{\texttt{dist}}$ isn't empty}
        \State Increment \texttt{dist}
        \State $L_{\texttt{dist}} \gets \{\}$
        \ForAll{$\texttt{curr} \in L_{\texttt{dist} - 1}$}
            \ForAll{$n \in$ \texttt{curr}'s neighbors}
                \If{$n$ isn't explored}
                    \State $L_{\texttt{dist}} \gets L_{\texttt{dist}} \cup \{n\}$
                \EndIf
            \EndFor
        \EndFor

        \item[]
        \If{$L_{\texttt{dist}} = 1$}
            \State \Return the only element in $L_{\texttt{dist}}$
        \EndIf
    \EndWhile
\end{algorithmic}

\subsection*{Complexity}

This algorithm is a basic BFS.
The only modification is that it stops early if it sees that the current
$L_{\texttt{dist}}$ is of size exactly $1$, in which case it stops early.
Thus, we see that the overall time complexity is $O(m+n)$.

\pagebreak

\section{Butterfly Classification}

\subsection*{Algorithm}

\begin{algorithmic}[1]
    \State $\texttt{comp} \gets \text{array of size }n\text{, all nil}$
    \State $\texttt{currComp} \gets 0$
    \For{$b \gets 1, n$}
        \If{$\texttt{comp}[i]$ isn't nil}
            \State \textbf{continue}
        \EndIf

        \item[]
        \State $\texttt{comp}[b] \gets \texttt{currComp}$
        \State $\texttt{frontier} \gets \text{empty queue}$
        \State Add $b$ to \texttt{frontier}
        \While{\texttt{frontier} isn't empty}
            \State $\texttt{curr} \gets \text{popped front of }\texttt{frontier}$
            \ForAll{$n \in L_{\texttt{curr},\text{same}}$}
                \If{$\texttt{comp}[n]$ is nil}
                    \State $\texttt{comp}[n] = \texttt{currComp}$
                    \State Add $n$ to $\texttt{frontier}$
                \EndIf
            \EndFor
        \EndWhile
        \State Increment \texttt{currComp}
    \EndFor

    \item[]
    \For{$b \gets 1, n$}
        \ForAll{$n \in L_{\texttt{curr},\text{diff}}$}
            \If{$\texttt{comp}[b] \ne \texttt{comp}[n]$}
                \State \Return not consistent
            \EndIf
        \EndFor
    \EndFor
    \State \Return consistent
\end{algorithmic}

\subsection*{Complexity}

The first section does a DFS floodfill of all connected components.
Each edge ("same" judgement) is traversed at most once and each node (butterfly)
is explored at most once, so the complexity of this part is $O(n+m)$.

The second section does an $O(1)$ operation for all the "different" judgemenets,
so the complexity of that part is $O(m)$.
Combined with the first part, we have a total time complexity of $O(n+m)$.

\section{Number of Shortest Paths}

\subsection*{Algorithm}

\begin{algorithmic}[1]
    \State $L_0 \gets \{v\}$
    \State $\texttt{dist} \gets 0$
    \State $\texttt{numWays} \gets \text{array of size }n\text{, all }0$
    \State Mark $v$ as explored
    \State $\texttt{numWays}[v] \gets 1$

    \item[]
    \While{$w \notin L_{\texttt{dist}}$}
        \State Increment \texttt{dist}
        \State $L_{\texttt{dist}} \gets \{\}$
        \ForAll{$\texttt{curr} \in L_{\texttt{dist} - 1}$}
            \ForAll{$n \in$ \texttt{curr}'s neighbors}
                \If{$n$ isn't explored}
                    \State $L_{\texttt{dist}} \gets L_{\texttt{dist}} \cup \{n\}$
                    \State $\texttt{numWays}[n] \gets \texttt{numWays}[\texttt{curr}]$
                \ElsIf{$n \in L_{\texttt{dist}}$}
                    \State $\texttt{numWays}[n] \gets \texttt{numWays}[n] + \texttt{numWays}[\texttt{curr}]$
                \EndIf
            \EndFor
        \EndFor
    \EndWhile

    \item[]
    \State \Return $\texttt{numWays}[w]$
\end{algorithmic}

\subsection*{Complexity}

Once again, we have a standard BFS with the addition of the array \texttt{numWays}
that stores the number of shortest paths from $v$ to all other nodes.
If we store $L_{\texttt{dist}}$ with a hash set, we can do the membership check
in the else if statement in constant time.
Thus, this algorithm has the same time complexity as a standard BFS,
which is $O(m+n)$.

\pagebreak

\section{Births and Deaths}

\subsection*{Algorithm}

This problem reduces to topological sorting.

\begin{algorithmic}[1]
    \State $V \gets \{P_1, P_1', P_2, P_2', \cdots P_n, P_n'\}$
    \State $E \gets \{\}$
    \For{$p \gets 1, n$}
        \State $E \gets E \cup (P_p, P_p')$
    \EndFor

    \item[]
    \ForAll{$\texttt{fact} \in \texttt{facts}$}
        \If{\texttt{fact} is of the first type}
            \State $E \gets E \cup (P_i', P_j)$
        \ElsIf{\texttt{fact} is of the second type}
            \State $E \gets E \cup (P_i', P_j')$
        \ElsIf{\texttt{fact} is of the third type}
            \State $E \gets E \cup (P_i, P_j')$
            \State $E \gets E \cup (P_j, P_i')$
        \EndIf
    \EndFor

    \item[]
    \State Attempt to toposort $G = (V, E)$
    \If{valid ordering}
        \State $\texttt{allEvents} \gets []$
        \State $t \gets 0$
        \ForAll{$\texttt{event} \in \text{the given ordering}$}
            \If{\texttt{event} is $P_i$}
                \State Append $i$'s birth event at time $t$ to \texttt{allEvents}
            \ElsIf{\texttt{event} is $P_i'$}
                \State Append $i$'s death event at time $t$ to \texttt{allEvents}
            \EndIf
            \State $t \gets t + 1$
        \EndFor
        \State \Return \texttt{allEvents}
    \Else
        \State \Return inconsistent memories
    \EndIf
\end{algorithmic}

\subsection*{Complexity}

The graph we construct has $2n$ nodes and at most $2m$ edges,
where $m$ is the number of facts.
The toposort algorithm will thus run in $O(2n+2m)=O(n+m)$ time.

The remaining section where we transform the ordering into a
log of the births and deaths takes $O(n)$, since that's just
a simple for loop through all the nodes in the topolgocial ordering.
Thus, the entire algorithm runs in time $O(m+n)$.

\end{document}
